SVG: The Paper

### 2022-07-21 Analysis/index.Rmd
finally got the sup mat working, I think

```{r echo = TRUE}
# item weights pre-computed - see scripts/extract_item_weights_using_model.R
a <- readRDS("scratch/qjep_model_weights.rda") %>%
  filter(found != 1) # remove initial selections

@@

```{r fig.height = 6, fig.cap = "Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
# computed in xxxx.R
fit <- readRDS("scratch/qjep_model_fit.rda") %>%
  full_join(a_acc, by = c("observer", "condition")) %>%
  mutate(is_outlier = if_else(observer %in% c(35, 45), TRUE, FALSE))

@@

ggsave("../Figures/qjep_indiv_diff.pdf", 
       plt_a + plt_b + 
         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
```

@@

write_csv(timedat, "scratch/time_per_trial.csv")

m <- readRDS("scratch/time_model_acc_model.rds")

@@

```{r}
ggsave("../Figures/qjep_ex_paths.pdf",
      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]]), 
       width = 8, height = 8)

rm(trls_easy, trls_mid, trls_hard, plts, qs, plts1, plts2, plts3)
```

@@

```{r, fig.height=3.5, fig.cap = "(*left*) Histogram comparing the empirical path lengths to simulations from our fitted model. Difference indicates the human path length - the simulated path length. (*right*) Histogram comparing the median path lengths per participant.", message=FALSE}
path_lengths <- readRDS("scratch/path_lengths.rda") %>%
  rename(observer = "obs",
         condition = "cond",
         human = "human_path_length",
         model = "model_path_length") %>% 
  mutate(difference  = human - model) %>%
  pivot_longer(c(human, model, difference), names_to = "type", values_to = "path_length")

@@

```{r}
ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 3)
```

@@

m <- readRDS("scratch/init_sel_model.rds")

@@

create_post_plot("x") + create_post_plot("y") + plt_mu
ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```

@@

ggsave("../Figures/init_sel2_mdl.pdf", width = 10, height = 3.5)
```

@@

ggsave("../Figures/qjep_init_sel_preds.pdf", 
       plt1 / (plt2 + plt3)  + plot_layout(guides = "collect"),
       width = 10, height = 6)

>>>>

```{r echo = TRUE}
# item weights pre-computed - see scripts/extract_item_weights_using_model_clarke.R
a <- readRDS("scratch/qjep_model_weights.rda") %>%
  filter(found != 1) # remove initial selections

@@

```{r fig.height = 6, fig.cap = "Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
# computed in scripts/extract_item_weights_using_model_clarke.R
fit <- readRDS("scratch/qjep_model_fit.rda") %>%
  full_join(a_acc, by = c("observer", "condition")) %>%
  mutate(is_outlier = if_else(observer %in% c(35, 45), TRUE, FALSE))

@@

#ggsave("../Figures/qjep_indiv_diff.pdf", 
#       plt_a + plt_b + 
#         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
```

@@

#write_csv(timedat, "scratch/time_per_trial.csv")

# see scripts/fit_time_model.R for full model fitting
m <- readRDS("scratch/time_model_acc_model.rds")

@@

```{r}
#ggsave("../Figures/qjep_ex_paths.pdf",
#      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]]), 
#       width = 8, height = 8)

rm(trls_easy, trls_mid, trls_hard, qs, plts1, plts2, plts3)
```

@@

```{r, fig.height=3.5, fig.cap = "(*left*) Histogram comparing the empirical path lengths to simulations from our fitted model. Difference indicates the human path length - the simulated path length. (*right*) Histogram comparing the median path lengths per participant.", message=FALSE}
# see scripts/compute_empirical_paths.R
path_lengths <- readRDS("scratch/path_lengths.rda") %>%
  rename(observer = "obs",
         condition = "cond",
         human = "human_path_length",
         model = "model_path_length") %>% 
  mutate(difference  = human - model) %>%
  pivot_longer(c(human, model, difference), names_to = "type", values_to = "path_length")

@@

```{r}
#ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 3)
```

@@

# see scripts/testing_init_selection.R
m <- readRDS("scratch/init_sel_model.rds")

@@

create_post_plot("x") + create_post_plot("y") + plt_mu
#ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```

@@

#ggsave("../Figures/init_sel2_mdl.pdf", width = 10, height = 3.5)
```

@@

#ggsave("../Figures/qjep_init_sel_preds.pdf", 
#       plt1 / (plt2 + plt3)  + plot_layout(guides = "collect"),
#       width = 10, height = 6)
